European or American? A re-examination of the transatlantic influence over the IMF

### 2025-05-21 manuscript/manuscript.qmd
add hypotheses

---
title: European or American? A re-examination of the transatlantic influence over the IMF
date: last-modified
authors:
  - name: Dianyi Yang
    email: d.yang17@lse.ac.uk
    orcid: 0009-0004-4652-3429
    correspondence: true
format:
  #native: default
  #docx: default
  orcid-pdf:
    keep-tex: true
    number-sections: true
abstract: This is an abstract.
keywords: IMF, US hegemony, Europe
execute:
  echo: false
  warning: false
  error: false
  message: false
---

@@

>>>>

---
title: European or American? A re-examination of the transatlantic influence over the IMF
date: last-modified
authors:
  - name: Dianyi Yang
    email: d.yang17@lse.ac.uk
    orcid: 0009-0004-4652-3429
    correspondence: true
format:
  #native: default
  #docx: default
  orcid-pdf:
    keep-tex: true
    number-sections: true
    include-in-header:
      - text: |
          \newcommand{\centerstart}{\begin{center}}
          \newcommand{\centerend}{\end{center}}
          \usepackage{amsthm, thm-restate}
          \newtheorem{hyp}{Hypothesis}
          \newtheorem{subhyp}{Hypothesis}[hyp]
          \renewcommand{\thesubhyp}{\thehyp\alph{subhyp}}
abstract: This is an abstract.
keywords: IMF, US hegemony, Europe
execute:
  echo: false
  warning: false
  error: false
  message: false
---

@@

\begin{restatable}[$H_{1}$]{hyp}{hypmain}
\label{hyp-main}
The United States and Europe exert different levels of influence on IMF lending decisions.
\end{restatable}

```{=latex}
\setcounter{hyp}{2}
\begin{restatable}[$H_{2a}$]{subhyp}{hypus}
\label{hyp-us}
The United States exerts a statistically significant influence on IMF lending decisions, controlling for European influence.
\end{restatable}
\vspace{-1em} % remove vertical space
\begin{restatable}[$H_{2b}$]{subhyp}{hypeu}
\label{hyp-eu}
Europe exerts a statistically significant influence on IMF lending decisions, controlling for United States influence.
\end{restatable}
```
